On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-27 docs/mvfits_paper/mvf.tex
misc updates

The process begins by finding the single symbol (basis vector) that yields the most accurate model (e.g. in the sense of minimizing the least-squares error).

@@

In each new iteration, an all remaining symbols are added to the model one at a time, resulting in many trial models.

@@

When considering all trial models, the single models symbol which yields the greatest increase in model accuracy is kept for the subsequent greedy iteration.

@@

The forward process is to end when the model accuracy, or changes thereof, pass a specified threshold.

@@

	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }

>>>>

The process begins by finding the single symbol (basis vector) that yields the most accurate model in the sense of minimizing the least-squares error.

@@

In each subsequent iteration, remaining symbols are added to the model one at a time, resulting in many trial models, each with its own representation error.

@@

The the trial model with smallest representation error is kept for the next greedy iteration.

@@

This forward greedy process ends when the model accuracy, or changes thereof, passes a previously specified threshold.

@@

	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. (Top Left) Mixing coefficients for cases where $(\bar{\ell},\bar{m})=(\ell,m)$. The dashed horizontal intersects each curve at the Schwarzschild limit where $\jf=0$. (Top Right) Mixing coefficients where $(\bar{\ell},\bar{m})\neq(\ell,m)$. (Bottom Left and Right) Factional residuals for mixing coefficient fits. }
